\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-10-06 stlc-mechanized.tex
stuff

FInductive hasty : env -> tm -> ty -> Prop :=
| ht_unit : [@\dadada@]  | ht_var : [@\dadada@][@\hfill\codecomment{Typing rules}@]
| ht_abs  : [@\dadada@]  | ht_app : [@\dadada@].

@@

End STLC_fix.
\end{lstlisting}

>>>>

FInductive hasty : env -> tm -> ty -> Prop :=
| ht_var  : [@\dadada@][@\hfill\codecomment{Typing rules}@]
| ht_unit : \forall G, hasty G tm_unit ty_unit
| ht_abs  : [@\dadada@]
| ht_app  : [@\dadada@].

@@

End STLC_fix.
\end{lstlisting}
\medskip

\begin{lstlisting}[numbers=left,firstnumber=111]
Check STLC_fix.typesafe.
\end{lstlisting}
